\section{Background}

Concolic execution is a useful technique that uses both the concepts 
of concrete execution and symbolic execution. Concrete execution is
a fast testing strategy that relies on the input it is given to be 
effective. Generally, it can take random input to hopefully cover
all paths in question. However, this can lead to issues if the input
distribution doesn't cover all paths uniformly. If there are several
paths a program could take and one of them is taken on only one input
out of the entire input space, this can lead to an issue where that path
is never taken and is therefore never tested. Symbolic execution on the
other hand calculates all paths a program can take. This prevents this
issue of missing a path. Unfortunately, symbolic execution can be very
expensive. As path conditions become more complex, it is harder to 
solve the constraints that would produce the input to follow this path.
With concolic execution, the advantages of these two types of tools can
be leveraged against each other to produce a faster tool that checks more
program paths. 

Recent developments in concolic testing have looked into optimizing the
process of switching between the concrete and symbolic sides of the tool\cite{Wang:2018:TOC:3180155.3180177}.
By using the probability of a path being taken along with the cost of
solving the constraint of paths, a tool can find the optimal time to
evaluate a path using the concrete execution or the symbolic execution.
Deciding when to choose between these tools is still an open problem.
Currently, many tools, like KLEE \cite{cadar2008klee}, use various heuristics to 
decide when to proceed  symbolically or concretely. 

In recent years, tools like Badger \cite{Noller:2018:BCA:3213846.3213868}
and Driller \cite{stephens2016driller} have combined symbolic execution
with fuzzing tools. Fuzzers generate random input that should exercise
the paths of execution of a program. Since these tools may not exercise paths
with a low probability of execution, combing them with symbolic execution
tools creates a concolic testing engine.